---
title: "2001-SHP-Clean-30m-90m"
author: "Anna Talucci"
date: "8/4/2020"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

What is included in this script:

# Packages

```{r include=FALSE}
library(sp)
library(sf)
library(rgdal) # geospatial data
library(raster)
library(rgeos) # GIS Geometry
library(foreign) # deals with dbf files
library(dplyr)
library(spatialEco)
```




# Projections

WGS 84 need for gee
```{r}
wgs_proj =  "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs "

```

Equal Area projection for russia need for buffering hotspot data
https://gis.stackexchange.com/questions/264093/projection-for-russia-map

+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs 

```{r}
ee_russia = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs "
```


# Read in shapefile
```{r}
f30m = readOGR("../data/2001_test_30_90m_climate/2001_30m_fires.shp", "2001_30m_fires") 
f90m = readOGR("../data/2001_test_30_90m_climate/2001_90m_fires.shp", "2001_90m_fires") 
 
```


```{r}
plot(f30m)
plot(f90m)
```

# Reproject in Equal area

```{r}
f30m_ee = spTransform(f30m, CRS(ee_russia))
f90m_ee = spTransform(f90m, CRS(ee_russia))

```


# Remove holes inside polygons
```{r}
f30m_nh = remove.holes(f30m_ee)
f90m_nh = remove.holes(f90m_ee)

```



# Convert from sp to sf
```{r}
f30m_sf = st_as_sf(f30m_nh)
f90m_sf = st_as_sf(f90m_nh)

```



# Covert from Multipolygon to Polygon

```{r}
f30m_sf = st_cast(f30m_sf,"POLYGON")
f90m_sf = st_cast(f90m_sf,"POLYGON")

```


```{r}
dim(f30m_sf)
head(f30m_sf)
```

```{r}
dim(f90m_sf)
head(f90m_sf)
```


# Create attributes
- ID based on row number
- area in meters squared, area_m
- area in Hectares, area_ha
- Year of the burn, fire_yr

```{r}
f30m_at = f30m_sf %>% dplyr::mutate(ID_obj = row_number()) %>% dplyr::mutate(area_m = round(st_area(f30m_sf),1)) %>% dplyr::mutate(area_ha = round(area_m*0.0001, 1)) %>% dplyr::mutate(fire_yr = 2001) 

f90m_at = f90m_sf %>% dplyr::mutate(ID_obj = row_number()) %>% dplyr::mutate(area_m = round(st_area(f90m_sf),1)) %>% dplyr::mutate(area_ha = round(area_m*0.0001, 1)) %>% dplyr::mutate(fire_yr = 2002) 
```


```{r}

head(f30m_at$area_ha)
min(f30m_at$area_ha)
max(f30m_at$area_ha)
```

```{r}

head(f90m_at$area_ha)
min(f90m_at$area_ha)
max(f90m_at$area_ha)
```

## Removed fires less than 400 ha

```{r}
f30m_ha = filter(f30m_at, as.numeric(f30m_at$area_ha) >= 400)
f90m_ha = filter(f90m_at, as.numeric(f90m_at$area_ha) >= 400)

```


```{r}
min(f30m_ha$area_ha)
max(f30m_ha$area_ha)

```


```{r}
min(f90m_ha$area_ha)
max(f90m_ha$area_ha)

```

# Reproject to WGS 84

```{r}
f30m_wgs = st_transform(f30m_ha, CRS( wgs_proj))
f90m_wgs = st_transform(f90m_ha, CRS( wgs_proj))

```


# Write to shapefile

```{r eval=FALSE, include=FALSE}
st_write(f30m_wgs, "../outputs/clean-shapefile-2001/30m_fires2001.shp", driver="ESRI Shapefile") 
st_write(f90m_wgs, "../outputs/clean-shapefile-2001/90m_fires2001.shp", driver="ESRI Shapefile")  
```



