---
title: "GIS-test"
author: "Anna Talucci"
date: "1/8/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

What is included in this script:

# Packages

```{r include=FALSE}
library(sp)
library(sf)
library(rgdal) # geospatial data
library(raster)
library(rgeos) # GIS Geometry
library(foreign) # deals with dbf files
library(dplyr)
```

# Creat Bounding Box for FLARE
```{r}


coords = matrix(c(118.94, 72.26,
               171.0, 72.26,
               171.0, 60.0, 
               118.94, 60.0), 
             ncol = 2, byrow = TRUE)


P1 = Polygon(coords)
Ps1 = SpatialPolygons(list(Polygons(list(P1), ID = "a")), proj4string=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))
```

```{r}
plot(Ps1, axes = TRUE)
```
```{r eval=FALSE, include=FALSE}
Ps2 = st_as_sf(Ps1) 
```

## Write bounding box to shapefile
```{r eval=FALSE, include=FALSE}
st_write(Ps2, "../outputs/FLARE_bbox.shp", driver="ESRI Shapefile")  # create to a shapefile 

```

# Read in hotspot data
```{r}
hotspot = readOGR("../data/hotspot_data/DL_FIRE_M6_2003/fire_archive_2003.shp", "fire_archive_2003") 
```

convert from sp to sf
```{r}
hotspot_sf = st_as_sf(hotspot) 
```


need to convert hotspot data to equal area projection in order to buffer. THis will allow to buffer by meters.

```{r eval=FALSE, include=FALSE}
plot(Ps1)
plot(hotspot, add= TRUE)
```

## Equal Area projection for russia
https://gis.stackexchange.com/questions/264093/projection-for-russia-map

+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs 



```{r}
newproj = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs "
```

```{r}
hotspot_sf_ee = st_transform(hotspot_sf, CRS( "+proj=laea +lat_0=90 +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs"))
```

```{r}
hotspot_sp_ee = spTransform(hotspot, CRS( "+proj=laea +lat_0=90 +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs"))
```

```{r}
Ps1_sp_ee = spTransform(Ps1, CRS( "+proj=laea +lat_0=90 +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs"))
```

```{r}
st_crs(hotspot_sf_ee)
```

```{r}
Ps2_ee = st_transform(Ps2, CRS( "+proj=laea +lat_0=90 +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs"))
```

```{r}
st_crs(Ps2_ee)
```

```{r}
plot(st_crop(hotspot_sf_ee, Ps2_ee))

```

## Reduce hotspot data to FLARE  BBox

```{r}

```

```{r}
hotspot_sp_ee_subset <- hotspot_sp_ee[Ps1_sp_ee, ]
```
```{r eval=FALSE, include=FALSE}
hotspot_subset <- hotspot[Ps1, ]
```

```{r}
hotspot_sf_ee_subset <- hotspot_sf_ee[Ps2_ee, ]
```

```{r eval=FALSE, include=FALSE}
buf <- buffer(hotspot_subset, width = 1000, filename = "../outputs/buffer_hotspot_2003", dissolve = TRUE)
```

## Buffer the subsetted hotspot data

width of gBuffer depends on the projection; the projection for hotspot data units of degrees 0.01 represents about 1km when in WGS 84 projection
```{r eval=FALSE, include=FALSE}
buf1 <- gBuffer(hotspot_subset, width = 0.01, capStyle="ROUND", joinStyle="ROUND")
```


```{r eval=FALSE, include=FALSE}
buf1 <- gBuffer(hotspot_subset, width = 0.01, capStyle="ROUND", joinStyle="ROUND")
```

```{r}
st_crs(hotspot_sf_ee_subset)$units
```

```{r eval=FALSE, include=FALSE}
hotspot_sp_ee_subset_buf <- gBuffer(hotspot_sp_ee_subset, width = 1000, capStyle="ROUND", joinStyle="ROUND")
```

```{r }
hotspot_sf_ee_subset_buf <- st_buffer(hotspot_sf_ee_subset, dist = 1000, endCapStyle="ROUND", joinStyle="ROUND")
```

```{r}
plot(hotspot_sp_ee_subset_buf)
```

```{r}
plot(hotspot_sf_ee_subset_buf)
```


## Write buffer to shapfirle

```{r eval=FALSE, include=FALSE}
st_write(hotspot_subset, "../outputs/Hotspots_2003.shp", driver="ESRI Shapefile")  # create to a shapefile 

```

#################
```{r eval=FALSE, include=FALSE}
hotspot_subset <- hotspot[Ps1, ]
```


```{r eval=FALSE, include=FALSE}
plot(Ps1)
plot(hotspot_subset, add= TRUE)
```



```{r eval=FALSE, include=FALSE}
writeOGR(obj = buf, dsn = "../outputs", layer = "buffer_hotspot_2003", driver = "ESRI Shapefile")
```

```{r eval=FALSE, include=FALSE}
plot(buf)
```

