---
title: "GIS-test"
author: "Anna Talucci"
date: "1/8/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

What is included in this script:

# Packages

```{r include=FALSE}
library(sp)
library(sf)
library(rgdal) # geospatial data
library(raster)
library(rgeos) # GIS Geometry
library(foreign) # deals with dbf files
library(dplyr)
```

# Projections
```{r}
wgs_proj =  "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs "

```



# Creat Bounding Box for FLARE

```{r}


coords = matrix(c(118.94, 72.26,
               171.0, 72.26,
               171.0, 60.0, 
               118.94, 60.0), 
             ncol = 2, byrow = TRUE)


P1 = Polygon(coords)
Ps1 = SpatialPolygons(list(Polygons(list(P1), ID = "a")), proj4string=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))
```

```{r}
plot(Ps1, axes = TRUE)
```
```{r}
Ps2 = st_as_sf(Ps1) 
```

## Write bounding box to shapefile

```{r eval=FALSE, include=FALSE}
st_write(Ps2, "../outputs/FLARE_bbox.shp", driver="ESRI Shapefile")  # create to a shapefile 

```

# Read in hotspot data

```{r}
hotspot = readOGR("../data/hotspot_data/DL_FIRE_M6_2003/fire_archive_2003.shp", "fire_archive_2003") 
```


```{r}
head(hotspot)
```

convert from sp to sf

```{r}
hotspot_sf = st_as_sf(hotspot) 
```

```{r}
head(hotspot_sf)
```


need to convert hotspot data to equal area projection in order to buffer. THis will allow to buffer by meters.


## Equal Area projection for russia
https://gis.stackexchange.com/questions/264093/projection-for-russia-map

+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs 


## Define Equal Area Projection
```{r}
ee_russia = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs "
```



```{r}
hotspot_sp_ee = spTransform(hotspot, CRS(ee_russia))
```

```{r}
Ps1_sp_ee = spTransform(Ps1, CRS( ee_russia))
```






## Reduce hotspot data to FLARE  BBox


```{r}
hotspot_sp_ee_subset <- hotspot_sp_ee[Ps1_sp_ee, ]
```

```{r eval=FALSE, include=FALSE}
hotspot_subset <- hotspot[Ps1, ]
```

```{r eval=FALSE, include=FALSE}
hotspot_sf_ee_subset <- hotspot_sf_ee[Ps2_ee, ]
```


```{r eval=FALSE, include=FALSE}
st_crs(hotspot_sf_ee_subset)$units
```

## 1km buffer
```{r}
hotspot_sp_ee_subset_1k <- gBuffer(hotspot_sp_ee_subset, width = 1000, capStyle="ROUND", joinStyle="ROUND")
```

```{r}
head(hotspot_sp_ee_subset_1k)
```

```{r}
plot(hotspot_sp_ee_subset_1k)
```

## Remove holes?
```{r}
 plot(remove.holes(hotspot_sp_ee_subset_1k))
```

```{r}
hotspot_sp_ee_1k_noholes = remove.holes(hotspot_sp_ee_subset_1k)
```

```{r}
hotspot_sp_1k_noholes_wgs = spTransform(hotspot_sp_ee_1k_noholes , CRS( "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs "))
```

```{r eval=FALSE, include=FALSE}
hotspot2003_1k_wgs84_noholes = st_as_sf(hotspot_sp_1k_noholes_wgs) 
```

```{r}
head(hotspot2003_1k_wgs84_noholes)
```

```{r eval=FALSE, include=FALSE}
st_write(hotspot2003_1k_wgs84_noholes, "../outputs/hotspot2003_1k_wgs84_noholes.shp", driver="ESRI Shapefile")  # create to a shapefile 

```





```{r}
hotspot_sp_ee_subset_buf_wgs = spTransform(hotspot_sp_ee_subset_buf, CRS( "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs "))
```

```{r}
plot(hotspot_sp_ee_subset_buf_wgs)
```


```{r eval=FALSE, include=FALSE}
hotspot2003_1k_wgs84 = st_as_sf(hotspot_sp_ee_subset_buf_wgs) 
```


```{r eval=FALSE, include=FALSE}
st_write(hotspot2003_1k_wgs84, "../outputs/hotspot2003_1k_wgs84.shp", driver="ESRI Shapefile")  # create to a shapefile 

```




## 3k buffer 

```{r}
hotspot_sp_ee_subset_buf3k <- gBuffer(hotspot_sp_ee_subset, width = 3000, capStyle="ROUND", joinStyle="ROUND")
```


```{r eval=FALSE, include=FALSE}
plot(hotspot_sp_ee_subset_buf3k)
```
## Remove holes in polygons
```{r}
hotspot_sp_ee_3k_noholes = remove.holes(hotspot_sp_ee_subset_buf3k)
```

## reproject to WGS for GEE

```{r}
hotspot_sp_ee_noholes_3k_wgs = spTransform(hotspot_sp_ee_3k_noholes, CRS( wgs_proj))
```

## Sp to sf
```{r}
hotspot2003_3k_wgs84 = st_as_sf(hotspot_sp_ee_noholes_3k_wgs) 
```

## Write to file
```{r eval=FALSE, include=FALSE}
st_write(hotspot2003_3k_wgs84, "../outputs/hotspot2003_3k_wgs84.shp", driver="ESRI Shapefile")  # create to a shapefile 

```

```{r eval=FALSE, include=FALSE}
plot(hotspot_sp_ee_subset_buf3k_wgs)
```




## 1km buffer with sf
```{r }
hotspot_sf_ee_subset_buf <- st_buffer(hotspot_sf_ee_subset, dist = 1000, endCapStyle="ROUND", joinStyle="ROUND")
```

```{r}
plot(hotspot_sp_ee_subset_buf)
```


```{r}
plot(hotspot_sp_ee_subset_buf_wgs)
```





