---
title: "Clean Polygon data"
author: "Anna Talucci"
date: "2/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

What is included in this script:

# Packages

```{r include=FALSE}
library(sp)
library(sf)
library(rgdal) # geospatial data
library(raster)
library(rgeos) # GIS Geometry
library(foreign) # deals with dbf files
library(dplyr)
library(spatialEco)
```




# Projections

WGS 84 need for gee
```{r}
wgs_proj =  "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs "

```

Equal Area projection for russia need for buffering hotspot data
https://gis.stackexchange.com/questions/264093/projection-for-russia-map

+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs 

```{r}
ee_russia = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs "
```


# Read in shapefile

```{r}
f01 = readOGR("../data/shapefile/2001_fires.shp", "2001_fires") 
f02 = readOGR("../data/shapefile/2002_fires.shp", "2002_fires") 
f03 = readOGR("../data/shapefile/2003_fires.shp", "2003_fires")
f04 = readOGR("../data/shapefile/2004_fires.shp", "2004_fires") 
f05 = readOGR("../data/shapefile/2005_fires.shp", "2005_fires") 
```

```{r}
f06 = readOGR("../data/shapefile/2006_fires.shp", "2006_fires") 
f07 = readOGR("../data/shapefile/2007_fires.shp", "2007_fires") 
f08 = readOGR("../data/shapefile/2008_fires.shp", "2008_fires")
f09 = readOGR("../data/shapefile/2009_fires.shp", "2009_fires") 
f10 = readOGR("../data/shapefile/2010_fires.shp", "2010_fires") 
```

```{r}
f11 = readOGR("../data/shapefile/2011_fires.shp", "2011_fires") 
f12 = readOGR("../data/shapefile/2012_fires.shp", "2012_fires") 
f13 = readOGR("../data/shapefile/2013_fires.shp", "2013_fires")
f14 = readOGR("../data/shapefile/2014_fires.shp", "2014_fires") 
f15 = readOGR("../data/shapefile/2015_fires.shp", "2015_fires") 
```

```{r}
f16 = readOGR("../data/shapefile/2016_fires.shp", "2016_fires") 
f17 = readOGR("../data/shapefile/2017_fires.shp", "2017_fires") 
f18 = readOGR("../data/shapefile/2018_fires.shp", "2018_fires")

f19 = readOGR("../data/shapefile/2019_fires.shp", "2019_fires")
f20 = readOGR("../data/shapefile/2020_fires.shp", "2020_fires")
 
```

```{r}
plot(f03)
```

# Reproject in Equal area

```{r}
f01_ee = spTransform(f01, CRS(ee_russia))
f02_ee = spTransform(f02, CRS(ee_russia))
f03_ee = spTransform(f03, CRS(ee_russia))
f04_ee = spTransform(f04, CRS(ee_russia))
f05_ee = spTransform(f05, CRS(ee_russia))
```

```{r}
f06_ee = spTransform(f06, CRS(ee_russia))
f07_ee = spTransform(f07, CRS(ee_russia))
f08_ee = spTransform(f08, CRS(ee_russia))
f09_ee = spTransform(f09, CRS(ee_russia))
f10_ee = spTransform(f10, CRS(ee_russia))
```


```{r}
f11_ee = spTransform(f11, CRS(ee_russia))
f12_ee = spTransform(f12, CRS(ee_russia))
f13_ee = spTransform(f13, CRS(ee_russia))
f14_ee = spTransform(f14, CRS(ee_russia))
f15_ee = spTransform(f15, CRS(ee_russia))
```

```{r}
f16_ee = spTransform(f16, CRS(ee_russia))
f17_ee = spTransform(f17, CRS(ee_russia))
f18_ee = spTransform(f18, CRS(ee_russia))
f19_ee = spTransform(f19, CRS(ee_russia))
f20_ee = spTransform(f20, CRS(ee_russia))
```

# Remove holes inside polygons
```{r}
f01_nh = remove.holes(f01_ee)
f02_nh = remove.holes(f02_ee)
f03_nh = remove.holes(f03_ee)
f04_nh = remove.holes(f04_ee)
f05_nh = remove.holes(f05_ee)
```


```{r}
f06_nh = remove.holes(f06_ee)
f07_nh = remove.holes(f07_ee)
f08_nh = remove.holes(f08_ee)
f09_nh = remove.holes(f09_ee)
f10_nh = remove.holes(f10_ee)
```

```{r}
f11_nh = remove.holes(f11_ee)
f12_nh = remove.holes(f12_ee)
f13_nh = remove.holes(f13_ee)
f14_nh = remove.holes(f14_ee)
f15_nh = remove.holes(f15_ee)
```

```{r}
f16_nh = remove.holes(f16_ee)
f17_nh = remove.holes(f17_ee)
f18_nh = remove.holes(f18_ee)

f19_nh = remove.holes(f19_ee)
f20_nh = remove.holes(f20_ee)
```

# Convert from sp to sf
```{r}
f01_sf = st_as_sf(f01_nh)
f02_sf = st_as_sf(f02_nh)
f03_sf = st_as_sf(f03_nh)
f04_sf = st_as_sf(f04_nh)
f05_sf = st_as_sf(f05_nh)
```

```{r}
f06_sf = st_as_sf(f06_nh)
f07_sf = st_as_sf(f07_nh)
f08_sf = st_as_sf(f08_nh)
f09_sf = st_as_sf(f09_nh)
f10_sf = st_as_sf(f10_nh)
```

```{r}
f11_sf = st_as_sf(f11_nh)
f12_sf = st_as_sf(f12_nh)
f13_sf = st_as_sf(f13_nh)
f14_sf = st_as_sf(f14_nh)
f15_sf = st_as_sf(f15_nh)
```

```{r}
f16_sf = st_as_sf(f16_nh)
f17_sf = st_as_sf(f17_nh)
f18_sf = st_as_sf(f18_nh)


f19_sf = st_as_sf(f19_nh)
f20_sf = st_as_sf(f20_nh)
```


# Covert from Multipolygon to Polygon

```{r}
f01_sf = st_cast(f01_sf,"POLYGON")
f02_sf = st_cast(f02_sf,"POLYGON")
f03_sf = st_cast(f03_sf,"POLYGON")
f04_sf = st_cast(f04_sf,"POLYGON")
f05_sf = st_cast(f05_sf,"POLYGON")
```

```{r}
f06_sf = st_cast(f06_sf,"POLYGON")
f07_sf = st_cast(f07_sf,"POLYGON")
f08_sf = st_cast(f08_sf,"POLYGON")
f09_sf = st_cast(f09_sf,"POLYGON")
f10_sf = st_cast(f10_sf,"POLYGON")
```

```{r}
f11_sf = st_cast(f11_sf,"POLYGON")
f12_sf = st_cast(f12_sf,"POLYGON")
f13_sf = st_cast(f13_sf,"POLYGON")
f14_sf = st_cast(f14_sf,"POLYGON")
f15_sf = st_cast(f15_sf,"POLYGON")
```

```{r}
f16_sf = st_cast(f16_sf,"POLYGON")
f17_sf = st_cast(f17_sf,"POLYGON")
f18_sf = st_cast(f18_sf,"POLYGON")
f19_sf = st_cast(f19_sf,"POLYGON")
f20_sf = st_cast(f20_sf,"POLYGON")
```

```{r}
dim(f03_sf)
head(f03_sf)
```



# Create attributes
- ID based on row number
- area in meters squared, area_m
- area in Hectares, area_ha
- Year of the burn, fire_yr

```{r}
f01_at = f01_sf %>% dplyr::mutate(ID_obj = row_number()) %>% dplyr::mutate(area_m = round(st_area(f01_sf),1)) %>% dplyr::mutate(area_ha = round(area_m*0.0001, 1)) %>% dplyr::mutate(fire_yr = 2001) 
f02_at = f02_sf %>% dplyr::mutate(ID_obj = row_number()) %>% dplyr::mutate(area_m = round(st_area(f02_sf),1)) %>% dplyr::mutate(area_ha = round(area_m*0.0001, 1)) %>% dplyr::mutate(fire_yr = 2002) 
f03_at = f03_sf %>% dplyr::mutate(ID_obj = row_number()) %>% dplyr::mutate(area_m = round(st_area(f03_sf),1)) %>% dplyr::mutate(area_ha = round(area_m*0.0001, 1)) %>% dplyr::mutate(fire_yr = 2003) 
f04_at = f04_sf %>% dplyr::mutate(ID_obj = row_number()) %>% dplyr::mutate(area_m = round(st_area(f04_sf),1)) %>% dplyr::mutate(area_ha = round(area_m*0.0001, 1)) %>% dplyr::mutate(fire_yr = 2004) 
f05_at = f05_sf %>% dplyr::mutate(ID_obj = row_number()) %>% dplyr::mutate(area_m = round(st_area(f05_sf),1)) %>% dplyr::mutate(area_ha = round(area_m*0.0001, 1)) %>% dplyr::mutate(fire_yr = 2005) 
```

```{r}
f06_at = f06_sf %>% dplyr::mutate(ID_obj = row_number()) %>% dplyr::mutate(area_m = round(st_area(f06_sf),1)) %>% dplyr::mutate(area_ha = round(area_m*0.0001, 1)) %>% dplyr::mutate(fire_yr = 2006) 
f07_at = f07_sf %>% dplyr::mutate(ID_obj = row_number()) %>% dplyr::mutate(area_m = round(st_area(f07_sf),1)) %>% dplyr::mutate(area_ha = round(area_m*0.0001, 1)) %>% dplyr::mutate(fire_yr = 2007) 
f08_at = f08_sf %>% dplyr::mutate(ID_obj = row_number()) %>% dplyr::mutate(area_m = round(st_area(f08_sf),1)) %>% dplyr::mutate(area_ha = round(area_m*0.0001, 1)) %>% dplyr::mutate(fire_yr = 2008) 
f09_at = f09_sf %>% dplyr::mutate(ID_obj = row_number()) %>% dplyr::mutate(area_m = round(st_area(f09_sf),1)) %>% dplyr::mutate(area_ha = round(area_m*0.0001, 1)) %>% dplyr::mutate(fire_yr = 2009) 
f10_at = f10_sf %>% dplyr::mutate(ID_obj = row_number()) %>% dplyr::mutate(area_m = round(st_area(f10_sf),1)) %>% dplyr::mutate(area_ha = round(area_m*0.0001, 1)) %>% dplyr::mutate(fire_yr = 2010) 
```


```{r}
f11_at = f11_sf %>% dplyr::mutate(ID_obj = row_number()) %>% dplyr::mutate(area_m = round(st_area(f11_sf),1)) %>% dplyr::mutate(area_ha = round(area_m*0.0001, 1)) %>% dplyr::mutate(fire_yr = 2011) 
f12_at = f12_sf %>% dplyr::mutate(ID_obj = row_number()) %>% dplyr::mutate(area_m = round(st_area(f12_sf),1)) %>% dplyr::mutate(area_ha = round(area_m*0.0001, 1)) %>% dplyr::mutate(fire_yr = 2012) 
f13_at = f13_sf %>% dplyr::mutate(ID_obj = row_number()) %>% dplyr::mutate(area_m = round(st_area(f13_sf),1)) %>% dplyr::mutate(area_ha = round(area_m*0.0001, 1)) %>% dplyr::mutate(fire_yr = 2013) 
f14_at = f14_sf %>% dplyr::mutate(ID_obj = row_number()) %>% dplyr::mutate(area_m = round(st_area(f14_sf),1)) %>% dplyr::mutate(area_ha = round(area_m*0.0001, 1)) %>% dplyr::mutate(fire_yr = 2014) 
f15_at = f15_sf %>% dplyr::mutate(ID_obj = row_number()) %>% dplyr::mutate(area_m = round(st_area(f15_sf),1)) %>% dplyr::mutate(area_ha = round(area_m*0.0001, 1)) %>% dplyr::mutate(fire_yr = 2015) 
```

```{r}
f16_at = f16_sf %>% dplyr::mutate(ID_obj = row_number()) %>% dplyr::mutate(area_m = round(st_area(f16_sf),1)) %>% dplyr::mutate(area_ha = round(area_m*0.0001, 1)) %>% dplyr::mutate(fire_yr = 2016) 
f17_at = f17_sf %>% dplyr::mutate(ID_obj = row_number()) %>% dplyr::mutate(area_m = round(st_area(f17_sf),1)) %>% dplyr::mutate(area_ha = round(area_m*0.0001, 1)) %>% dplyr::mutate(fire_yr = 2017) 
f18_at = f18_sf %>% dplyr::mutate(ID_obj = row_number()) %>% dplyr::mutate(area_m = round(st_area(f18_sf),1)) %>% dplyr::mutate(area_ha = round(area_m*0.0001, 1)) %>% dplyr::mutate(fire_yr = 2018) 
f19_at = f19_sf %>% dplyr::mutate(ID_obj = row_number()) %>% dplyr::mutate(area_m = round(st_area(f19_sf),1)) %>% dplyr::mutate(area_ha = round(area_m*0.0001, 1)) %>% dplyr::mutate(fire_yr = 2019) 
f20_at = f20_sf %>% dplyr::mutate(ID_obj = row_number()) %>% dplyr::mutate(area_m = round(st_area(f20_sf),1)) %>% dplyr::mutate(area_ha = round(area_m*0.0001, 1)) %>% dplyr::mutate(fire_yr = 2020) 
```

```{r}

head(f03_at$area_ha)
min(f03_at$area_ha)
max(f03_at$area_ha)
```

## Removed fires less than 400 ha

```{r}
f01_ha = filter(f01_at, as.numeric(f01_at$area_ha) >= 400)
f02_ha = filter(f02_at, as.numeric(f02_at$area_ha) >= 400)
f03_ha = filter(f03_at, as.numeric(f03_at$area_ha) >= 400)
f04_ha = filter(f04_at, as.numeric(f04_at$area_ha) >= 400)
f05_ha = filter(f05_at, as.numeric(f05_at$area_ha) >= 400)
```

```{r}
f06_ha = filter(f06_at, as.numeric(f06_at$area_ha) >= 400)
f07_ha = filter(f07_at, as.numeric(f07_at$area_ha) >= 400)
f08_ha = filter(f08_at, as.numeric(f08_at$area_ha) >= 400)
f09_ha = filter(f09_at, as.numeric(f09_at$area_ha) >= 400)
f10_ha = filter(f10_at, as.numeric(f10_at$area_ha) >= 400)
```


```{r}
f11_ha = filter(f11_at, as.numeric(f11_at$area_ha) >= 400)
f12_ha = filter(f12_at, as.numeric(f12_at$area_ha) >= 400)
f13_ha = filter(f13_at, as.numeric(f13_at$area_ha) >= 400)
f14_ha = filter(f14_at, as.numeric(f14_at$area_ha) >= 400)
f15_ha = filter(f15_at, as.numeric(f15_at$area_ha) >= 400)
```

```{r}
f16_ha = filter(f16_at, as.numeric(f16_at$area_ha) >= 400)
f17_ha = filter(f17_at, as.numeric(f17_at$area_ha) >= 400)
f18_ha = filter(f18_at, as.numeric(f18_at$area_ha) >= 400)

f19_ha = filter(f19_at, as.numeric(f19_at$area_ha) >= 400)
f20_ha = filter(f20_at, as.numeric(f20_at$area_ha) >= 400)

```

```{r}
min(f03_ha$area_ha)
max(f03_ha$area_ha)

```

# Reproject to WGS 84

```{r}
f01_wgs = st_transform(f01_ha, CRS( wgs_proj))
f02_wgs = st_transform(f02_ha, CRS( wgs_proj))
f03_wgs = st_transform(f03_ha, CRS( wgs_proj))
f04_wgs = st_transform(f04_ha, CRS( wgs_proj))
f05_wgs = st_transform(f05_ha, CRS( wgs_proj))
```

```{r}
f06_wgs = st_transform(f06_ha, CRS( wgs_proj))
f07_wgs = st_transform(f07_ha, CRS( wgs_proj))
f08_wgs = st_transform(f08_ha, CRS( wgs_proj))
f09_wgs = st_transform(f09_ha, CRS( wgs_proj))
f10_wgs = st_transform(f10_ha, CRS( wgs_proj))
```

```{r}
f11_wgs = st_transform(f11_ha, CRS( wgs_proj))
f12_wgs = st_transform(f12_ha, CRS( wgs_proj))
f13_wgs = st_transform(f13_ha, CRS( wgs_proj))
f14_wgs = st_transform(f14_ha, CRS( wgs_proj))
f15_wgs = st_transform(f15_ha, CRS( wgs_proj))
```

```{r}
f16_wgs = st_transform(f16_ha, CRS( wgs_proj))
f17_wgs = st_transform(f17_ha, CRS( wgs_proj))
f18_wgs = st_transform(f18_ha, CRS( wgs_proj))
f19_wgs = st_transform(f19_ha, CRS( wgs_proj))
f20_wgs = st_transform(f20_ha, CRS( wgs_proj))
```

# Write to shapefile

```{r eval=FALSE, include=FALSE}
st_write(f01_wgs, "../outputs/clean-shapefile/fires2001.shp", driver="ESRI Shapefile") 
st_write(f02_wgs, "../outputs/clean-shapefile/fires2002.shp", driver="ESRI Shapefile")  
st_write(f03_wgs, "../outputs/clean-shapefile/fires2003.shp", driver="ESRI Shapefile")  
st_write(f04_wgs, "../outputs/clean-shapefile/fires2004.shp", driver="ESRI Shapefile")  
st_write(f05_wgs, "../outputs/clean-shapefile/fires2005.shp", driver="ESRI Shapefile")  
```

```{r eval=FALSE, include=FALSE}
st_write(f06_wgs, "../outputs/clean-shapefile/fires2006.shp", driver="ESRI Shapefile") 
st_write(f07_wgs, "../outputs/clean-shapefile/fires2007.shp", driver="ESRI Shapefile")  
st_write(f08_wgs, "../outputs/clean-shapefile/fires2008.shp", driver="ESRI Shapefile")  
st_write(f09_wgs, "../outputs/clean-shapefile/fires2009.shp", driver="ESRI Shapefile")  
st_write(f10_wgs, "../outputs/clean-shapefile/fires2010.shp", driver="ESRI Shapefile")  
```


```{r eval=FALSE, include=FALSE}
st_write(f11_wgs, "../outputs/clean-shapefile/fires2011.shp", driver="ESRI Shapefile") 
st_write(f12_wgs, "../outputs/clean-shapefile/fires2012.shp", driver="ESRI Shapefile")  
st_write(f13_wgs, "../outputs/clean-shapefile/fires2013.shp", driver="ESRI Shapefile")  
st_write(f14_wgs, "../outputs/clean-shapefile/fires2014.shp", driver="ESRI Shapefile")  
st_write(f15_wgs, "../outputs/clean-shapefile/fires2015.shp", driver="ESRI Shapefile")  
```


```{r eval=FALSE, include=FALSE}
st_write(f16_wgs, "../outputs/clean-shapefile/fires2016.shp", driver="ESRI Shapefile") 
st_write(f17_wgs, "../outputs/clean-shapefile/fires2017.shp", driver="ESRI Shapefile")  
st_write(f18_wgs, "../outputs/clean-shapefile/fires2018.shp", driver="ESRI Shapefile")  

st_write(f19_wgs, "../outputs/clean-shapefile/fires2019.shp", driver="ESRI Shapefile") 
st_write(f20_wgs, "../outputs/clean-shapefile/fires2020.shp", driver="ESRI Shapefile") 
```

# Write to KML

```{r eval=FALSE, include=FALSE}
st_write(f01_wgs, "../outputs/clean-kml/fires2001.kml", driver="KML") 
st_write(f02_wgs, "../outputs/clean-kml/fires2002.kml", driver="KML")  
st_write(f03_wgs, "../outputs/clean-kml/fires2003.kml", driver="KML")  
st_write(f04_wgs, "../outputs/clean-kml/fires2004.kml", driver="KML")  
st_write(f05_wgs, "../outputs/clean-kml/fires2005.kml", driver="KML")  
```

```{r eval=FALSE, include=FALSE}
st_write(f06_wgs, "../outputs/clean-kml/fires2006.kml", driver="KML") 
st_write(f07_wgs, "../outputs/clean-kml/fires2007.kml", driver="KML")  
st_write(f08_wgs, "../outputs/clean-kml/fires2008.kml", driver="KML")  
st_write(f09_wgs, "../outputs/clean-kml/fires2009.kml", driver="KML")  
st_write(f10_wgs, "../outputs/clean-kml/fires2010.kml", driver="KML")  
```


```{r eval=FALSE, include=FALSE}
st_write(f11_wgs, "../outputs/clean-kml/fires2011.kml", driver="KML") 
st_write(f12_wgs, "../outputs/clean-kml/fires2012.kml", driver="KML")  
st_write(f13_wgs, "../outputs/clean-kml/fires2013.kml", driver="KML")  
st_write(f14_wgs, "../outputs/clean-kml/fires2014.kml", driver="KML")  
st_write(f15_wgs, "../outputs/clean-kml/fires2015.kml", driver="KML")  
```


```{r eval=FALSE, include=FALSE}
st_write(f16_wgs, "../outputs/clean-kml/fires2016.kml", driver="KML") 
st_write(f17_wgs, "../outputs/clean-kml/fires2017.kml", driver="KML")  
st_write(f18_wgs, "../outputs/clean-kml/fires2018.kml", driver="KML")  
```

# Subset to Yakutsk BBox


```{r}
yak_bbox = readOGR("../data/bbox/yakutsk_bbox.shp", "yakutsk_bbox") 
```

```{r}
plot(yak_bbox, axes = TRUE)
```

```{r warning=FALSE}
f01_yak = st_crop(f01_wgs, yak_bbox)
f02_yak = st_crop(f02_wgs, yak_bbox)
f03_yak = st_crop(f03_wgs, yak_bbox)
f04_yak = st_crop(f04_wgs, yak_bbox)
f05_yak = st_crop(f05_wgs, yak_bbox)

```
```{r warning=FALSE}
f06_yak = st_crop(f06_wgs, yak_bbox)
f07_yak = st_crop(f07_wgs, yak_bbox)
f08_yak = st_crop(f08_wgs, yak_bbox)
f09_yak = st_crop(f09_wgs, yak_bbox)
f10_yak = st_crop(f10_wgs, yak_bbox)
```

```{r warning=FALSE}
f11_yak = st_crop(f11_wgs, yak_bbox)
f12_yak = st_crop(f12_wgs, yak_bbox)
f13_yak = st_crop(f13_wgs, yak_bbox)
f14_yak = st_crop(f14_wgs, yak_bbox)
f15_yak = st_crop(f15_wgs, yak_bbox)
```

```{r warning=FALSE}
f16_yak = st_crop(f16_wgs, yak_bbox)
f17_yak = st_crop(f17_wgs, yak_bbox)
f18_yak = st_crop(f18_wgs, yak_bbox)
```

```{r}
plot(yak_bbox, axes = TRUE)
plot(f01_yak, add=TRUE)
```

# Write to shapefile

```{r eval=FALSE, warning=FALSE, include=FALSE}
st_write(f01_yak, "../outputs/yakutsk-shape/fires2001.shp", driver="ESRI Shapefile") 
st_write(f02_yak, "../outputs/yakutsk-shape/fires2002.shp", driver="ESRI Shapefile")  
st_write(f03_yak, "../outputs/yakutsk-shape/fires2003.shp", driver="ESRI Shapefile")  
st_write(f04_yak, "../outputs/yakutsk-shape/fires2004.shp", driver="ESRI Shapefile")  
st_write(f05_yak, "../outputs/yakutsk-shape/fires2005.shp", driver="ESRI Shapefile")  
```

```{r eval=FALSE, warning=FALSE, include=FALSE}
st_write(f06_yak, "../outputs/yakutsk-shape/fires2006.shp", driver="ESRI Shapefile") 
st_write(f07_yak, "../outputs/yakutsk-shape/fires2007.shp", driver="ESRI Shapefile")  
st_write(f08_yak, "../outputs/yakutsk-shape/fires2008.shp", driver="ESRI Shapefile")  
st_write(f09_yak, "../outputs/yakutsk-shape/fires2009.shp", driver="ESRI Shapefile")  
st_write(f10_yak, "../outputs/yakutsk-shape/fires2010.shp", driver="ESRI Shapefile")  
```


```{r eval=FALSE, warning=FALSE, include=FALSE}
st_write(f11_yak, "../outputs/yakutsk-shape/fires2011.shp", driver="ESRI Shapefile") 
st_write(f12_yak, "../outputs/yakutsk-shape/fires2012.shp", driver="ESRI Shapefile")  
st_write(f13_yak, "../outputs/yakutsk-shape/fires2013.shp", driver="ESRI Shapefile")  
st_write(f14_yak, "../outputs/yakutsk-shape/fires2014.shp", driver="ESRI Shapefile")  
st_write(f15_yak, "../outputs/yakutsk-shape/fires2015.shp", driver="ESRI Shapefile")  
```


```{r eval=FALSE, warning=FALSE, include=FALSE}
st_write(f16_yak, "../outputs/yakutsk-shape/fires2016.shp", driver="ESRI Shapefile") 
st_write(f17_yak, "../outputs/yakutsk-shape/fires2017.shp", driver="ESRI Shapefile")  
st_write(f18_yak, "../outputs/yakutsk-shape/fires2018.shp", driver="ESRI Shapefile")  
```

# Write to KML

```{r eval=FALSE, include=FALSE}
st_write(f01_yak, "../outputs/yakutsk-kml/fires2001.kml", driver="KML") 
st_write(f02_yak, "../outputs/yakutsk-kml/fires2002.kml", driver="KML")  
st_write(f03_yak, "../outputs/yakutsk-kml/fires2003.kml", driver="KML")  
st_write(f04_yak, "../outputs/yakutsk-kml/fires2004.kml", driver="KML")  
st_write(f05_yak, "../outputs/yakutsk-kml/fires2005.kml", driver="KML")  
```

```{r eval=FALSE, include=FALSE}
st_write(f06_yak, "../outputs/yakutsk-kml/fires2006.kml", driver="KML") 
st_write(f07_yak, "../outputs/yakutsk-kml/fires2007.kml", driver="KML")  
st_write(f08_yak, "../outputs/yakutsk-kml/fires2008.kml", driver="KML")  
st_write(f09_yak, "../outputs/yakutsk-kml/fires2009.kml", driver="KML")  
st_write(f10_yak, "../outputs/yakutsk-kml/fires2010.kml", driver="KML")  
```


```{r eval=FALSE, include=FALSE}
st_write(f11_yak, "../outputs/yakutsk-kml/fires2011.kml", driver="KML") 
st_write(f12_yak, "../outputs/yakutsk-kml/fires2012.kml", driver="KML")  
st_write(f13_yak, "../outputs/yakutsk-kml/fires2013.kml", driver="KML")  
st_write(f14_yak, "../outputs/yakutsk-kml/fires2014.kml", driver="KML")  
st_write(f15_yak, "../outputs/yakutsk-kml/fires2015.kml", driver="KML")  
```


```{r eval=FALSE, include=FALSE}
st_write(f16_yak, "../outputs/yakutsk-kml/fires2016.kml", driver="KML") 
st_write(f17_yak, "../outputs/yakutsk-kml/fires2017.kml", driver="KML")  
st_write(f18_yak, "../outputs/yakutsk-kml/fires2018.kml", driver="KML")  
```